---
title: "Regressionstest"
author: "Rebecca Folmer Schade"
date: "2023-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "..")
```

```{r}
# Loading packages
pacman::p_load(pacman, tidyverse, arsenal)

```

I have tried to do a regression test in two different ways: First I compare the two data sets directly - Are they the same? Where are they different?
Next, I do an examination of the individual variables to check if there are any outliers - and which of these outliers are one of the differences between the two data sets.  

### Load data

```{r}
#### Shouls I use file.path()?

# Load Consistency 1_0_0
con_00 <- read_csv2("../Data/Consistency 1_0_0.csv")
# Check dataframe
head(con_00)

# Load Consistency 1_0_1
con_01 <- read_csv2("../Data/Consistency 1_0_1.csv")
# Check dataframe
head(con_01)

```

### Rename columns

```{r}
#===> Lets start with the easy stuff
# Create new objects 
clean_00 <- con_00
clean_01 <- con_01

# Remove _ in start of colnames 
colnames(clean_00) <- gsub("^[[:punct:]]+", "", colnames(clean_00))
colnames(clean_01) <- gsub("^[[:punct:]]+", "", colnames(clean_01))

# Change punctuation
colnames(clean_00) <- gsub("[[:punct:]]+", "_", colnames(clean_00))
colnames(clean_01) <- gsub("[[:punct:]]+", "_", colnames(clean_01))

# gsub("([[:lower:]])([[:upper:]])", "\\1_\\2", strn)

#===> And now for the hard one
# Define function
rep_num <- function(idx, col_list) {
  start_idx <- idx
  end_idx <- idx + 126
  sub <- cn[start_idx:end_idx]
  prefix <- str_extract(sub[1], "CF.+")
  rep_with <- sprintf("%s_\\1", prefix)
  sub[2:127] <- gsub("(^\\d+)(.+)", rep_with, sub[2:127])
  
  return(sub)
}

# Define list of colnames
col_list_00 <- colnames(clean_00)
col_list_01 <- colnames(clean_01)

# Get index of CF columns
idx_00 <- grep(".+CF.+", col_list_00)
idx_01 <- grep(".+CF.+", col_list_01)

# modify column list 
l_00 <- lapply(idx_00, function(x) rep_num(x, col_list_00))
col_list_00[idx_00[1]:length(col_list_00)] <- unlist(l_00)
#
l_01 <- lapply(idx_01, function(x) rep_num(x, col_list_01))
col_list_01[idx_01[1]:length(col_list_01)] <- unlist(l_01)
col_list_01

# Rename columns
colnames(clean_00) <- col_list_00
colnames(clean_01) <- col_list_01

```


## Look at data structure

First I Check that the two data sets are the same size.

```{r}
# Check how many columns they have
ncol(clean_00)
ncol(clean_01)
# > There are more columns in the old data set
ncol(clean_00) - ncol(clean_01)
# > There are 127 more columns in the old dataset

# What about the rows? 
nrow(clean_00)
nrow(clean_01)
# > The newer data set seems to be missing a row

```

Which ones?

```{r}
# Which ID's do not appear in the other data set?  
clean_00$RecordIdentifier[!clean_00$RecordIdentifier %in% clean_01$RecordIdentifier]
# > Row "F44936EAB043EDB60F3AA8A522D2D70548410BE6" it is! this fella is missing!

# Which columns are different? 
setdiff(colnames(clean_00), colnames(clean_01))
setdiff(colnames(clean_01), colnames(clean_00))
# Let's save them
diff_col <- setdiff(colnames(clean_00), colnames(clean_01))

```

## One to one comparison

Lets remove the rows and columns that don't appear in con_01 so we can compare the data sets mere exactly.  

```{r}
# Select all other columns
comp_00 <- clean_00 %>% select(-matches(diff_col))
# > Now the two dataframes have the same nr. of columns!

# Get rid of the extra row
comp_00 <- subset(comp_00, RecordIdentifier != "F44936EAB043EDB60F3AA8A522D2D70548410BE6")

# Let's check
sum(!comp_00$RecordIdentifier %in% clean_01$RecordIdentifier)
sum(!clean_01$RecordIdentifier %in% comp_00$RecordIdentifier) # > I checked this now, but in the future, it might be a good idea to do this
# > Yes! All rows are present! 

```
Now for the more fine-grained comparison

```{r}
# Let's have a look at different compariason methods
summary(comparedf(comp_00, clean_01))[7]
summary(comparedf(comp_00, clean_01))[6]
summary(comparedf(comp_00, clean_01))[2]
# These two are interesting

# Let's try to save it as a table
comp <- summary(comparedf(comp_00, clean_01))[6]
comp_tbl <- as_tibble(comp$diffs.byvar.table)
colnames(comp_tbl) <- gsub("[[:punct:]]", "_", colnames(comp_tbl))

# Let's filter it!
diff_tbl <- comp_tbl %>% filter(n > 0)
# > Looks like we have 570 columns with different values.

# What about rows? 
d <- summary(comparedf(comp_00, clean_01))
length(unique(d$diffs.table$..row.names..))
# There are differences in every row 


```

## Summary statistics

```{r}
# Let's have a look at the summary stats
sum_stats_00 <- tail(comp_00, n = 6)
sum_stats_01 <- tail(clean_01, n = 6)

# In theory, we could find all the columns with different values by checking if the sums are the same
sum_list_00 = sum_stats_00[1, ] %>% t() %>% as.list() %>% unlist()
sum_list_01 = sum_stats_01[1, ] %>% t() %>% as.list() %>% unlist()

# Assign a dummy variable
a[is.na(a)] <- 999

sum(sum_list_00 != sum_list_01, na.rm = TRUE)

length(sum_list_00)

NA == 5

all.equal(sum_list_00, sum_list_01)
all.equal(sum_stats_00, sum_stats_01)

```

####==========> TODO
- Compare the built-in summary statistics

- Sanity-check the built-in summary statistics 
- Not the next part, compare nr. of outliers in the different datsets. 






